---
title: "cn-HPC validation in external cohort"
output: html_notebook
---

```{r}
# Import libraries
suppressPackageStartupMessages({
    library(openxlsx)
    library(ggplot2)
    library(ggpubr)
    library(broom)
    library(plyr)
    library(uwot)
    library(stringr)
    library(rhdf5)
    library(RColorBrewer)
    library(ggrepel)
    library(scran)
    library(rjson)
    library(class)
    library(reshape2)
    library(varhandle)
    library(dplyr)
  library(gtools)
  library(glue)
  library(pROC)
})
```

Load cluster CSV with UMAP.
```{r}
output_parent_dir <- "/gpfs/scratch/leh06/NivoPembro_Results/Figures_240516/"
if (!file.exists(output_parent_dir)){
    dir.create(output_parent_dir)
}
# Load the TCGA-LUAD UMAP
load(glue("{output_parent_dir}analysis_data.RData"))
```

Load cluster csv output by HPL pipeline for the external cohort.
```{r}
cluster_csv_immuno <- read.csv("/gpfs/data/tsirigoslab/home/leh06/Histomorphological-Phenotype-Learning/results/BarlowTwins_3/tcga_luad_cell_224px_20x/h224_w224_n3_zdim128/survival/adatas/nyuimmuno_cell_224px_20x_luad_he_complete_metadata_leiden_1p0__fold1.csv")

clin_info_immuno <- read.csv("/gpfs/data/tsirigoslab/home/leh06/PathGAN/clinical_data/nivo_pembro_clinical_041724.csv")
clin_info_immuno$samples <- clin_info_immuno$Case.1510.ID..
clin_info_immuno$slides <- clin_info_immuno$ScanID

h5_data_immuno <- h5read(file = "/gpfs/data/tsirigoslab/home/leh06/Histomorphological-Phenotype-Learning/results/BarlowTwins_3/nyuimmuno_cell_224px_20x_luad/h224_w224_n3_zdim128/hdf5_nyuimmuno_cell_224px_20x_luad_he_complete_metadata.h5", name = "/")

latent_projs_immuno <- h5_data_immuno$img_z_latent
latent_projs_immuno <- t(latent_projs_immuno)
print(dim(latent_projs_immuno))

h5_clin_immuno <- data.frame(slides = as.integer(h5_data_immuno$slides), 
                             tiles = h5_data_immuno$tiles, 
                             metastaticsite = h5_data_immuno$metastaticsite,
                             befafttr = h5_data_immuno$befafttr)
```

Load csv file with centroids and cell types.
```{r}
centroid_df_immuno <- read.csv("/gpfs/data/tsirigoslab/home/leh06/Rscripts/centroid_df_224px_20x_immuno_full_info.csv")
centroid_df_immuno$slides <- as.integer(centroid_df_immuno$slides)
centroid_df_immuno <- left_join(h5_clin_immuno, centroid_df_immuno, by = c("slides","tiles"))

indexes_primary <- c(1:nrow(h5_clin_immuno))[(h5_clin_immuno$metastaticsite %in% c("LUNG", "PLEURA")) & (h5_clin_immuno$befafttr == "Before")]
indexes_metastatic <- c(1:nrow(h5_clin_immuno))[(!h5_clin_immuno$metastaticsite %in% c("LUNG", "PLEURA")) & (h5_clin_immuno$befafttr == "Before")]
indexes_full <- c(1:nrow(h5_clin_immuno))[(h5_clin_immuno$befafttr == "Before")]
```




Plot UMAP from the TCGA-LUAD UMAP.

```{r}
umap_nyuimmuno_primary <- uwot::umap_transform(latent_projs_immuno[indexes_primary,], umap_tcga, verbose = TRUE)
umap_nyuimmuno_primary_df <- data.frame(x = umap_nyuimmuno_primary[,1], 
                           y = umap_nyuimmuno_primary[,2])
png(file = glue("{output_parent_dir}umap_nyuimmuno_primary.png"), width = 10, height = 10, unit = "in", res = 200)
print(ggplot(umap_nyuimmuno_primary_df, aes(x=x, y = y)) + 
        geom_point(alpha = 0.05,size = 0.5)+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_blank(), axis.text.x = element_blank(),
axis.title = element_blank(),
axis.text.y = element_blank(),
  axis.ticks = element_blank(),
legend.position = "none")+
  labs(x = "UMAP1",
       y = "UMAP2"))
dev.off()
```

Visualization: Plot UMAP with cn-HPCs. 
```{r}
umap_kmeans_immuno_primary_df <- left_join(h5_clin_immuno[indexes_primary,], cluster_csv_immuno, by = c("slides", "tiles"))
umap_kmeans_immuno_primary_df <- cbind(umap_kmeans_immuno_primary_df, umap_nyuimmuno_primary_df)
umap_kmeans_immuno_primary_df <- left_join(umap_kmeans_immuno_primary_df, centroid_df_immuno, by = c("slides", "tiles"))
umap_kmeans_immuno_primary_df$samples <- left_join(umap_kmeans_immuno_primary_df, clin_info_immuno, by = "slides")$samples.y
for (i in celltypes$type){
  label <- celltypes$labels[celltypes$type == i]
  umap_kmeans_immuno_primary_df$CellType <- str_replace_all(as.character(umap_kmeans_immuno_primary_df$CellType), as.character(i), label)
}
umap_kmeans_immuno_primary_df$CellType <- factor(umap_kmeans_immuno_primary_df$CellType)
umap_kmeans_immuno_primary_df$cluster <- umap_kmeans_immuno_primary_df[,grep("leiden",names(umap_kmeans_immuno_primary_df))]

umap_kmeans_immuno_primary_df <- umap_kmeans_immuno_primary_df[!is.na(umap_kmeans_immuno_primary_df$cluster),]
umap_kmeans_immuno_primary_df$cluster <- factor(umap_kmeans_immuno_primary_df$cluster)

label.df <- data.frame(cluster=levels(umap_kmeans_immuno_primary_df$cluster),label=levels(umap_kmeans_immuno_primary_df$cluster))
label.df_2 <- umap_kmeans_immuno_primary_df %>%
  group_by(cluster) %>%
  summarize(x = mean(x), y = mean(y)) %>%
  left_join(label.df)


png(file = glue("{output_parent_dir}umap_clusters_nyu_primary.png"), width = 10, height = 10, unit = "in", res = 200)
print(ggplot(umap_kmeans_immuno_primary_df, aes(x=x, y = y, color = cluster)) + geom_point(size = 0.5, alpha = 0.05)+
        scale_color_manual(values = custom_palette)+
theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.text.x = element_blank(),
axis.text.y = element_blank(),
axis.ticks = element_blank(),
axis.line=element_blank(), axis.title = element_blank(),
legend.position = "none")+
labs(x = "UMAP1",
     y = "UMAP2",
     color = "Cluster") +ggrepel::geom_label_repel(data = label.df_2,aes(label = label), size = 5, alpha = 1))
dev.off()
```

Create cell compositions (histogram): for each cluster a bar, and each bar contains colors.
```{r}
cbbPalette <- c("lightgrey", "#CC79A7", "#F0E442", "#000000", "#009E73","#0072B2")
# All cells
df <- melt(umap_kmeans_immuno_primary_df[,c("cluster","others",  "connective", "inflammatory", "necrosis", "non_neoplastic","neoplastic")],id = "cluster")
df$cluster <- paste0("cn-HPC",factor(df[,"cluster"]))
df_tiles <- melt(table(umap_kmeans_immuno_primary_df[,c("cluster","CellType")]))
df_tiles$cluster <- paste0("C",factor(df_tiles[,"cluster"]))
brks <- c(0.0, 0.25, 0.50, 0.75, 1.0)

df <- df %>%
summarize(total = sum(value),
          .by =c(cluster,variable))

df$total[is.na(df$total)] <- 0

totals_tiles <- df_tiles %>%
group_by(cluster) %>%
summarize(total_tiles = sum(value))

totals <- df %>%
summarize(total = sum(total),
          .by =c(cluster))

totals <- totals %>%
  left_join(totals_tiles,
            by = "cluster")

ordered_clusters <- df[df$variable == "neoplastic",c("cluster", "total")]
totals <- totals[match(ordered_clusters$cluster, totals$cluster),]
ordered_clusters$total <- ordered_clusters$total/totals$total*100
ordered_clusters <- ordered_clusters$cluster[order(ordered_clusters$total, decreasing = T)]

df$cluster <- factor(df$cluster, levels = ordered_clusters)
totals$cluster <- factor(totals$cluster, levels = ordered_clusters)

df$variable <- factor(df$variable, levels = c("others",  "connective", "inflammatory", "necrosis",  "non_neoplastic", "neoplastic"))

png(file = glue("{output_parent_dir}cluster_cell_composition_immuno_primary.png"), width = 30, height = 10, units = 'in', res = 200)
print(ggplot(df, aes(fill=variable, y=total, x=cluster)) +
        scale_fill_manual(values=cbbPalette) +  
  geom_bar(position="fill", stat="identity") + 
  geom_text(aes(cluster, -0.03 , label = paste0("n=", total), fill = NULL), data = totals,  size=3.5) +
    theme_bw() +
theme(axis.title.y = element_blank(), axis.title.x = element_blank(),
      axis.ticks.y = element_blank(), legend.title = element_blank(),
      text = element_text(size = 40), axis.text.x = element_text(angle = 90,size = 40)) +
labs(y = "Distribution of all cell types in tiles (%)", fill = "Cell types") +
scale_y_continuous(labels = scales::percent)) 
dev.off()
```

Wilcoxon analysis of clusters with Best Overall response
```{r}
# Prepare clinical information for NYU-Immuno.
tilecomp.df.bor.primary <- data.frame(matrix(nrow = 0, ncol = 4, dimnames = list(NULL, c("Cluster", "Patient", "TileComposition", "Category"))))
resptest.bor.df <- data.frame(matrix(nrow = 0, ncol = 4, dimnames = list(NULL, c("Cluster", "pvalue", "resp_Median", "prog_Median"))))
 
labels_full <- umap_kmeans_immuno_primary_df[,c("slides", "tiles", "samples", "outcome_label", "cluster")]
labels_full$bor <- left_join(labels_full, unique(clin_info_immuno[,c("samples","BOR")]), by = "samples")$BOR

categories <- c("response", "progression")

nb_tile_patients <- data.frame(table(labels_full$samples))
names(nb_tile_patients) <- c("samples", "total_nb_tiles")
nb_tile_patients <- join(nb_tile_patients, labels_full, by = "samples", type = "left", match = "first")[,c("samples","total_nb_tiles", "bor")]

for (c in unique(labels_full$cluster)){
  # responders
  count_df_resp <- table(labels_full[labels_full$cluster == c & labels_full$bor == "response", c("samples", "bor")])
  nb_tile_patients_resp <- nb_tile_patients[nb_tile_patients$bor == "response",]
  if (nrow(count_df_resp)>0){
    count_df_resp <- data.frame(count_df_resp)
    count_df_resp <- join(count_df_resp, nb_tile_patients_resp, by = c("samples", "bor"), type = "left", match = "first")
    count_df_resp$tile_composition <- count_df_resp$Freq/count_df_resp$total_nb_tiles*100
    count_df_resp <- rbind(count_df_resp, data.frame(samples = nb_tile_patients_resp$samples[! nb_tile_patients_resp$samples %in% count_df_resp$samples], bor = rep("response", nrow(nb_tile_patients_resp) - nrow(count_df_resp)), Freq = rep(0, nrow(nb_tile_patients_resp) - nrow(count_df_resp)), total_nb_tiles = nb_tile_patients_resp$total_nb_tiles[!nb_tile_patients_resp$samples %in% count_df_resp$samples], tile_composition = rep(0, nrow(nb_tile_patients_resp) - nrow(count_df_resp))))
  } else {
    count_df_resp <- data.frame(samples = nb_tile_patients_resp$samples, bor = rep("response", nrow(nb_tile_patients_resp)), Freq = rep(0, nrow(nb_tile_patients_resp)), total_nb_tiles = nb_tile_patients_resp$total_nb_tiles, tile_composition = rep(0, nrow(nb_tile_patients_resp)))
  }

  # non-responders
  count_df_prog <- table(labels_full[labels_full$cluster == c & labels_full$bor == "progression", c("samples", "bor")])
  nb_tile_patients_prog <- nb_tile_patients[nb_tile_patients$bor == "progression",]
  if (nrow(count_df_prog)>0){
    count_df_prog <- data.frame(count_df_prog)
    count_df_prog <- join(count_df_prog, nb_tile_patients_prog, by = c("samples", "bor"), type = "left", match = "first")
    count_df_prog$tile_composition <- count_df_prog$Freq/count_df_prog$total_nb_tiles*100
    count_df_prog <- rbind(count_df_prog, data.frame(samples = nb_tile_patients_prog$samples[! nb_tile_patients_prog$samples %in% count_df_prog$samples], bor = rep("progression", nrow(nb_tile_patients_prog) - nrow(count_df_prog)), Freq = rep(0, nrow(nb_tile_patients_prog) - nrow(count_df_prog)), total_nb_tiles = nb_tile_patients_prog$total_nb_tiles[! nb_tile_patients_prog$samples %in% count_df_prog$samples], tile_composition = rep(0, nrow(nb_tile_patients_prog) - nrow(count_df_prog))))
  } else {
    count_df_prog <- data.frame(samples = nb_tile_patients_prog$samples, bor = rep("progression", nrow(nb_tile_patients_prog)), Freq = rep(0, nrow(nb_tile_patients_prog)), total_nb_tiles = nb_tile_patients_prog$total_nb_tiles, tile_composition = rep(0, nrow(nb_tile_patients_prog)))
  }
  # wilcoxon
  wilcox <- wilcox.test(count_df_resp$tile_composition, count_df_prog$tile_composition, exact = FALSE)

  # Add tile compositions to dataframe
  tilecomp.df.bor.primary <- rbind(tilecomp.df.bor.primary, data.frame(Cluster = rep(c, nrow(count_df_resp)), Patient = count_df_resp$samples, TileComposition = count_df_resp$tile_composition, Category = count_df_resp$bor))
  tilecomp.df.bor.primary <- rbind(tilecomp.df.bor.primary, data.frame(Cluster = rep(c, nrow(count_df_prog)), Patient = count_df_prog$samples, TileComposition = count_df_prog$tile_composition, Category = count_df_prog$bor))


 # Add pvalues to dataframe
  resptest.bor.df <- rbind(resptest.bor.df, data.frame(Cluster = paste0("cn-HPC", c),
                                               pvalue = wilcox$p.value,
                                               resp_Median = median(count_df_resp$tile_composition),
                                               prog_Median = median(count_df_prog$tile_composition)))
}

# Boxplots
barplot.df <- data.frame(matrix(nrow = 0, ncol = 3, dimnames = list(NULL, c("Cluster", "Percentage", "Group"))))

resp_samples <- unique(labels_full$samples[labels_full$bor == "response"])

prog_samples <- unique(labels_full$samples[labels_full$bor == "progression"])

for (c in unique(labels_full$cluster)){

  # responders
  value_resp <- length(tilecomp.df.bor.primary$Patient[(tilecomp.df.bor.primary$Cluster == c) & (tilecomp.df.bor.primary$TileComposition > 0) &
                                             (tilecomp.df.bor.primary$Patient %in% resp_samples)])
  percent_resp <- value_resp/length(resp_samples)*100
  barplot.df <- rbind(barplot.df, data.frame(Cluster = c, Percentage = percent_resp, Group = "resp", Value = paste0("n=",value_resp)))

  value_prg <- length(tilecomp.df.bor.primary$Patient[(tilecomp.df.bor.primary$Cluster == c) & (tilecomp.df.bor.primary$TileComposition > 0) &
                                             (tilecomp.df.bor.primary$Patient %in% prog_samples)])
  percent_prg <- value_prg/length(prog_samples)*100
  barplot.df <- rbind(barplot.df, data.frame(Cluster = c, Percentage = percent_prg, Group = "prog", Value = paste0("n=",value_prg)))
}

boxplot.df <- tilecomp.df.bor.primary
give.n <- function(x){
return(c(y = -8, label = length(x[x>0])))
}
boxplot.df$Cluster <- factor(paste0("cn-HPC", boxplot.df$Cluster), levels = paste0("cn-HPC",sort(as.integer(unique(boxplot.df$Cluster)))))

png(filename=glue("{output_parent_dir}boxplot_immuno_primary_bor.png"), res = 200, units = "in", width = 40, height = 5)
print(ggplot(boxplot.df,
     aes(x = Category,
         y = TileComposition,
         fill = Category)) + geom_boxplot() +
geom_jitter(shape=1, position=position_jitter(0.2)) +
scale_fill_manual(values=c("#00BFC4","#F8766D"))+ ylim(-10,100)+ ylab("Tile Percentage")+
facet_grid(. ~ Cluster) + theme_bw() + theme(legend.position = "none", axis.text.x = element_text(angle = 90), axis.title.x = element_blank(), text = element_text(size=30)) + stat_summary(fun.data = give.n, geom = "text", size = 5)+ stat_compare_means( aes(label = ..p.signif..), 
                      label.x = 1.5, label.y = 90, size = 10))
dev.off()


png(filename=glue("{output_parent_dir}boxplot_immuno_primary_bor_cnhpc23.png"), res = 200, units = "in", width = 5, height = 7)
print(ggplot(boxplot.df_2[boxplot.df_2$Cluster == "cn-HPC23",],
     aes(x = Category,
         y = TileComposition,
         fill = Category)) + geom_boxplot() +
geom_jitter(shape=1, position=position_jitter(0.2)) +
scale_fill_manual(values=c("#00BFC4","#F8766D"))+ ylim(0,70)+ ylab("Tile Percentage")+
facet_grid(~Cluster) + theme_bw() + theme(legend.position = "none", axis.text.x = element_text(angle = 90), axis.title.x = element_blank(), text = element_text(size=30)) + stat_compare_means( aes(label = ..p.signif..), 
                      label.x = 1.5, label.y = 65, size = 10)+ stat_compare_means(label = "p.format", method = "wilcox.test", tip.length = 0.01, size = 10,label.y = 60, label.x = 1.2))
dev.off()
```


Rank-based AUC for cn-HPC 23
```{r}
df <- tilecomp.df.bor.primary[tilecomp.df.bor.primary$Cluster == "23",]
ranks <- rank(df$TileComposition)
png(filename=glue("{output_parent_dir}HPC_23_auc_nyu_primary.png"), res = 200, units = "in", width = 10, height = 10)
plot(roc(df$Category, ranks), print.auc = TRUE)
dev.off()
```

Comparison with common LUAD driver mutations
Mutations for NYU-Immuno

```{r}
# Add age
pembro_age_df <- read.csv("/gpfs/data/tsirigoslab/home/leh06/PathGAN/clinical_data/S1801510EvaluationOf_DATA_LABELS_2021-03-17_1104_Pembro.csv")
nivo_age_df <- read.csv("/gpfs/data/tsirigoslab/home/leh06/PathGAN/clinical_data/S1801510EvaluationOf_DATA_LABELS_2021-03-17_1104_Nivo CORRECTED.csv")
```


```{r}
mutations_cols <- c("ALK..choice.Positive.", "BRAF..choice.Positive.", "EGFR..choice.Positive.", "ERBB2.HER.2..choice.Positive.", "KEAP.1..choice.Positive.", "KRAS..choice.Positive.", "PDL.1..choice.Positive.", "RET..choice.Positive.", "ROS.1..choice.Positive.", "STK.11..choice.Positive.", "MET..choice.Positive.")

for (c in mutations_cols){
  columns <- names(pembro_age_df)[grepl(c, names(pembro_age_df))]
  pembro_age_df[str_split(c, "\\.\\.", simplify = T)[,1]] <- apply(pembro_age_df[,columns], 1, function(x) {ifelse(any(x == "Checked"), 1, 0)})
  columns <- names(nivo_age_df)[grepl(c, names(nivo_age_df))]
  nivo_age_df[str_split(c, "\\.\\.", simplify = T)[,1]] <- apply(nivo_age_df[,columns], 1, function(x) {ifelse(any(x == "Checked"), 1, 0)})
}

clin_info_immuno <- left_join(clin_info_immuno, rbind(pembro_age_df[,c("Case.1510.ID..", "ALK", "BRAF", "EGFR", "ERBB2.HER.2", "KEAP.1", "KRAS", "PDL.1", "RET", "ROS.1", "STK.11", "MET")], nivo_age_df[,c("Case.1510.ID..", "ALK", "BRAF", "EGFR", "ERBB2.HER.2", "KEAP.1", "KRAS", "PDL.1", "RET", "ROS.1", "STK.11", "MET")]), by = "Case.1510.ID..")
```

```{r}
biomarkers <- c('ALK','BRAF','EGFR', 'ERBB2.HER.2', 'KEAP.1', 'KRAS', 'PDL.1','RET', 'ROS.1', 'STK.11', 'MET')
df <- clin_info_immuno[(clin_info_immuno$BefAftTr == 'Before') & (clin_info_immuno$MetastaticSite %in% c('PLEURA','LUNG') & (clin_info_immuno$BOR != 'Unknown')),c('samples','BOR', biomarkers)]
df <- unique(df)
df <- df %>% 
  mutate(BOR = replace(BOR, BOR == 'Response', 1),
         BOR = replace(BOR, BOR == 'Progression', 0))
df$BOR <- as.numeric(df$BOR)
df <- subset(df, select = -c(samples))

# Individual biomarkers
results <- data.frame(Biomarker=character(), AUC=numeric(), stringsAsFactors = FALSE)

for (b in biomarkers) {
  formula <- as.formula(paste("BOR ~", b))
  model <- glm(formula, data = df, family = binomial())
  probs <- predict(model, type = "response")
  
  roc_obj <- roc(df$BOR, probs)
  auc_val <- auc(roc_obj)
  
  results <- rbind(results, data.frame(Biomarker = b, AUC = auc_val))
}

print(results)


# All biomarkers 
# Fit logistic regression model
model <- glm(BOR ~ ., data = df, family = binomial())

# View model summary
summary(model)

# Predict probabilities
df$predicted_prob <- predict(model, type = "response")

# Predict binary outcome (threshold = 0.5)
df$predicted_class <- ifelse(df$predicted_prob > 0.5, 1, 0)

# Confusion matrix
print(table(Predicted = df$predicted_class, Actual = df$BOR))

# ROC and AUC
# if (!require("pROC")) install.packages("pROC")
# library(pROC)
roc_obj <- roc(df$BOR, df$predicted_prob)
auc_val <- auc(roc_obj)
plot(roc_obj,print.auc = TRUE, xlim = c(1,0), legacy.axes = TRUE)
```
